% \documentclass[a4paper,10pt]{article}
% \usepackage[utf8]{inputenc}
% \usepackage[pdftex]{graphicx}

\documentclass[conference]{IEEEtran}

% %\usepackage{todonotes}
\usepackage{amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{epstopdf}
%\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{soul}
\usepackage[tight,footnotesize]{subfigure}
\usepackage{url}

\usepackage{color}


% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% Title Page
\title{On the Integration of Heterogeneous Data Sources for the Collaborative Internet of Things}
\author{\IEEEauthorblockN{Federico Montori, Luca Bedogni, Luciano Bononi
\IEEEauthorblockA{
Department of Computer Science and Engineering (DISI)\\
University of Bologna, Italy\\
Email: \{federico.montori2, luca.bedogni4, luciano.bononi\}@unibo.it}}
}


\begin{document}
\maketitle

\begin{abstract}
The Internet of things is foreseen as one of the next imminent Internet revolutions, as many devices will seamlessly communicate together to provide new and exciting services to the end users. One of the challenges that the IoT has to face is about both the heterogeneity of the data available and the heterogeneity of the communication. In this paper we focus on the former, by presenting an architecture able to integrate data coming from different sources, including custom made deployments and government data. New services can be deployed directly by the end users, using reliable or unreliable data sources, and new processed data can be gathered by these services and used by others.

\end{abstract}

\input{introduction.tex}

\input{related.tex}

\input{opendata.tex}

\input{unification.tex}

\input{architecture.tex}

\section{Conclusions}
\label{sec:conclusions}

In this paper we have studied the challenging topic of data integration between heterogeneous data sources for the Internet of Things. We have considered open data coming both from reliable sources like Governmental agencies as well as unreliable sources, made available through open clouds such as ThingSpeak and SparkFun. We analyzed the differences, and proposed a new architecture to integrate them together, along with the ability to deliver custom made services to the end users, using both reliable and unreliable data.

Future works on this topic go through the integration of additional data sources, which will eventually provide a wider set of data. We also plan to use Natural Language Processing (NLP) techniques, as much of the work will then be devoted to the study of how to integrate heterogeneous data, together, which can be described using natural language by the users providing them.


%In this paper we showed how open data express their high potential in the ecosystem of data fusion and how we aim to manage them in order to integrate heterogeneous collaborative approaches within a global vision, by exploiting heterogeneous data sources.



\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{iot}
\end{document}          
